%!TEX root = ../report.tex
\chapter{Sprint Review}\label{chap:sprint3_end}
We have succeeded in accomplishing all user stories this sprint but missed a non-crucial task. In this chapter, we evaluate the tasks we planned to do and the sprint as a whole on a multi-project level.

\begin{chapterorganization}
  \item In \sectionref{sec:s3_goals} we evaluate how the sprint went and whether we reached our goals on a group level;
  \item in \sectionref{sec:s3_multiprj_review} we evaluate how the sprint went on the multi-project level.
\end{chapterorganization}

\section{Sprint Goals}\label{sec:s3_goals}
\begin{description}
  \item[Make Guidelines for Continuous Integration] We have fulfilled the desire of the developers for a clear central specification of the process. The specification is available on the Redmine Wiki, and resembles \chapterref{chap:sw_dev_method}. The specification is necessary as it is time consuming to explain it over and over, and because the process sometimes changes. A central wiki entry helps the developers keep up to date.
  \item[Add a Guide on How to Do UI Test] We have specified how to set up and run UI testing in a guide which is available on the Redmine Wiki. The guide links to the testing guide \parencite{AndroidUnit} of the Android Developer website, as it is clear and comprehensive. Our guide just adds details specific to the multi-project, e.g.\ how to initialize the database with dummy data.
  \item[Monkey Test] In this sprint, we have enabled monkey testing for all apps. We have created a new app for inserting dummy data into the local database.  This app is run before the app that must be monkey tested. In that way, apps can be run without downloading the real database, which can take 10 minutes or more. There already existed jobs in Jenkins for monkey testing, and these have been updated to use the dummy data. We did not manage to fulfill the task of setting up a subscription based notification system for developers, as we discovered report related tasks that we prioritized more highly than this task. In any case this task is actually not necessary to fulfill the user story --- it should not have been created in the first place.
  \item[Specify the Scrum Process Used] \group{1} approached us last sprint with an analysis of the development method. The analysis raised a number of critiques, which we discussed with \group{1}. From this discussion we, in collaboration with \group{1}, revised the development method. We specified how user stories are formulated and added new types of product backlog items.
\end{description}

\section{Multi-Project Sprint Review}\label{sec:s3_multiprj_review}
Up to the end of the sprint there were some issues regarding the Launcher app. An update of the database library had rendered the Launcher unusable. This meant increased workload at the end of the sprint to fix the issue. At the multi-project sprint review it is explained that the error had been there for a while, but was only discovered at the end of the sprint, as the \gui groups did not always use the newest version of each app. In addition, the \db PO mentions that other bugs were introduced because of a large merge with the master branch.

We reiterate the importance of performing daily integration with the master branch, to ensure that no major merges are performed that can introduce numerous errors. The semester coordinator also note the importance of \gui groups always using the latest versions of all apps to catch such errors as quickly as possible.
