\chapter{Servicing Developers}
This chapter describes our work with the two user stories related to prioritizing jobs in Jenkins, and downloading and installing all apps in an easy way. We have also identified several things the last sprints that can improve usability and avoid some common mistakes among developers with regards to using Git. Even though we do not have a user story to back this up, we decide to implement these minor things to improve the developer-friendliness and to avoid the common mistakes.

\begin{chapterorganization}
  \item in \sectionref{sec:jenkins_prio_queue} we identify and implement a way of prioritizing jobs in Jenkins, and compare various scheduling algorithms;
  \item in \sectionref{sec:appdownloadscript} we create scripts that developers can execute which will download the newest versions of all apps and install them onto a connected device;
  \item in \sectionref{sec:prereceivehook} we describe small usability improvements and mechanisms to avoid common mistakes when developers push to Git repositories;
  \item in \sectionref{sec:jenkins_doc} we describe how we document Jenkins targeting future developers of the Giraf project.
\end{chapterorganization}

\section{Jenkins Priority Queue}\label{sec:jenkins_prio_queue}
We have committed ourselves to setup a prioritized build queue on Jenkins, such that libraries have a higher priority than other jobs, such as apps. Developers do not want to wait for libraries to build when there are many apps in the queue. This is because libraries are released on Artifactory often, and waiting for them to be released blocks further development more than waiting for apps to build.

To solve this user story, we install a Jenkins plugin \parencite{jenkins-priority-plugin} which allows for a prioritized build queue. This plugin allows us to assign each Jenkins project a priority from one to five (where one is the highest priority). We select a scheduling algorithm which manages the way in which jobs are ordered.

\subsection{Scheduling Algorithms}
By introducing a priority queue, a number of potential problems arise. There is a risk of starvation, which means that high priority jobs take all resources such that jobs of lower priority are never run. The overall objective is to increase the average throughput of high priority jobs without making the low priority jobs starve.

The Jenkins plugin comes with three different scheduling algorithms:

\begin{description}
  \item[Absolute] The queue is strictly ordered by priority. The highest priority job is greedily selected every time a new job is to be executed.
  \item[Fair Queuing] Each priority group has a separate queue. Every time a job is requested the job is added to the queue of the priority group the job belongs to. The scheduler executes builds from each priority group in a round robin manner. This means that each group gets an equal amount of jobs executed, regardless of the distribution of jobs between groups.
  \item[Weighted Fair Queuing] Each priority has a separate queue and a ``bucket''. Every time a job is requested, it is added to the queue of the priority the job belongs to and its weight is added to the bucket corresponding to the priority of the job. The scheduler always selects a job from the priority with the lightest bucket. Each priority is weighted, so when a priority five build is enqueued, five times as much weight is added to the corresponding bucket than when a priority one build is enqueued. Because every priority has its own bucket, the jobs with priority five will eventually be started, as the bucket corresponding to priority one will get heavier than the bucket of priority five after five builds with priority one.
\end{description}

The absolute scheduling algorithm clearly improves the throughput of high priority jobs. However, there is a risk of starving jobs. The fair queuing algorithm, on the other hand, does not risk starving jobs, but also does not improve throughput for prioritized jobs. The weighted fair queuing algorithm distributes the resources among the different jobs based on their priorities. The throughput of high priority jobs is increased, and the throughput of low priority tasks is decreased, and the low priority tasks are still guaranteed to be run at some point. Because of this, we use the weighted fair queuing algorithm to make library jobs build faster than other jobs on Jenkins.

We give all libraries priority two by default, and all apps priority four. The Meta-Database library, however, has priority one, as the developers often wait for this specific library to complete.

\section{Easy App Download and Installation}\label{sec:appdownloadscript}
The user story \us{Easy Download and Installation of all Apps} describes that developers want to be able to easily install the most recent versions of all apps on their devices. To solve this problem, we develop a script which downloads the most recent apps from the FTP server. The solution must work on both Unix systems and Windows without any additional software.

\subsection{Keeping Track of Newest Apps}
When new applications are built on Jenkins, we upload them to the GIRAF FTP server. We extend this upload functionality to also create a symbolic link to the newest version in a \mono{newest\_releases/} directory. This directory contains only one link per app, and thus allows us to avoid finding the newest release in a directory containing all releases. Thus we avoid having to search for the newest APK as we have previously done, simplifying the script. Now, we can simply download all files in this directory to have the most recent versions of all apps.

\subsection{Downloading and Installing Apps}
Because we keep track of the newest apps on the build server, only little work is to be done in the download script. Because of this, we allow ourselves to develop two different scripts: A Bash script for Unix and a Powershell script for Windows. These scripts first connect to the FTP server and downloads the apps. Afterwards, it reinstalls each app on a connected device.

The Unix script can be seen in \listingref{lst:download_install_apks_unix}. We connect to the FTP with the \code{-i -n} options that disables prompting when downloading multiple files and disables auto login, respectively (line \ref{download_install_apks:ftp_start}). Being connected we specify that the files to be downloaded are binary, get all files in the newest releases directory and quit (lines \ref{download_install_apks:binary}--\ref{download_install_apks:quit}). We then install the downloaded APKs onto a connected device (lines \ref{download_install_apks:installing_start}--\ref{download_install_apks:installing_stop}). The Powershell script can be seen in \appendixref{app:download_and_install_apks_windows} and works similarly.

Because the scripts do not require any additional software and because they download and install all applications automatically, this solution comply with the conditions of satisfaction of the user story.

\begin{lstlisting}[language=bash,caption=Bash script that downloads and installs newest APKs,label=lst:download_install_apks_unix]
#!/bin/bash
ftp -i -n ftp://ftpuser:9scWKbP@cs-cust06-int.cs.aau.dk/newest_releases/ << EOF (*@\label{download_install_apks:ftp_start}@*)
    binary (*@\label{download_install_apks:binary}@*)
    mget * (*@\label{download_install_apks:mget}@*)
    quit (*@\label{download_install_apks:quit}@*)
EOF

COUNTER=0 (*@\label{download_install_apks:installing_start}@*)
for f in *.apk
do
    echo "Trying to Uninstall $f"
    adb uninstall ${f%'.apk'}
    echo "Installing $f"
    adb install -r "$f"
    COUNTER=$(expr $COUNTER + 1)
done (*@\label{download_install_apks:installing_stop}@*)
echo "Installed $COUNTER apps"
exit 0
\end{lstlisting}

\section{Pre-Receive Hook}\label{sec:prereceivehook}
During the latest sprints, we have discovered several times that developers have committed the database password on Git which causes everyone to change the database password. This is frustrating and time consuming, and for this reason we choose to implement a pre-receive Git hook which rejects a push containing the database password. This is not a user story but a refactoring of the version control system. A pre-receive hook is run every time something is pushed to the Git repository, but before the changes are applied (in contrast to the post-receive hook previously described). If the script returns a non-zero exit code, the commit is rejected.

As we develop this hook, we add a number of additional features. Overall, it checks for the following:
\begin{description}
  \item[Database Passwords] The database password is stored in a Java file called \mono{DatabaseCredentials.java}. Every database developer has this file locally and inserts it manually during development. On Jenkins, this file is automatically added to the project during build. Even though the file is part of the gitignore list, it is sometimes commited by mistake. If this file is contained anywhere in the push, it is rejected.
  \item[References to Local Dependencies] Sometimes, applications reference a \code{0.0-SNAPSHOT} version of a library, which is used to reference a library which is stored on the developer's computer. When Jenkins builds the project, it breaks because it cannot find the library. Such mistakes are avoided by checking for local dependency references.
  \item[Dynamic Dependency References] Dependencies can be declared with a dynamic version number (e.g.\ \code{1.4.+}). As described earlier, we discourage this as it removes the ability to backtrack exact dependency versions in a specific revision of a repository. We therefore check for such references as well and rejects the push of they are referenced.
  \item[Push Enabled] The script checks if there exists a file called \mono{git\_disabled} in the Jenkins home folder. If the file exists, we instantly reject the push. The contents of the file is returned to the developer when they try to push. One should write a message detailing why pushing is disabled in the file. This allows us to temporarily disable pushes to Git if we for example are restarting Jenkins, and let the developers know why it is disabled.
\end{description}
The full pre-receive Git hook code can be seen in \appendixref{sec:app_git_hook_pre}.

\section{Documenting Jenkins}\label{sec:jenkins_doc}
Next year the development of the multi-project will be taken over by the current 4\textsuperscript{th} semester software students. To ease the handover of the project we describe the Jenkins configuration, and installation in a reference document. The document can be seen in \appendixref{app:jenkins_structure}. The document is an attempt to document all of our tacit knowledge of the Jenkins server in a complete record. The document includes how jobs are configured, general management of Jenins, and a description of files used for automation.